---
title: Analysis
description:
toc: true
authors: []
tags: []
categories: []
series: []
date: 2022-12-14T00:53:24-05:00
lastmod: 2022-12-14T00:53:24-05:00
featuredVideo:
featuredImage:
draft: false
---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(plotly)
library(tidyverse)
library(readr)
```

<font size="5"><b>Crime Association Analysis</font></b>


To continue testing our hypothesis that crime rate is associated with the migration pattern and whether race and income would influence such association, we visualized the patterns of robbery rate of the entire country, burglary rate of the entire country, and the proportion of people moved in and out of the state according to early (2000-2007) and late period (2010-2017). In the scatter plot, where the Y axis represents the proportion of the population moving in and out of the states, and  X axis represents the proportion of the crime rates (per 100,000 inhabitants). As the dots were scattered all over the place, we determined that there were no obvious associations between the two specific types of crime rate and the proportion of people moving in and out of the state. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
leave <- read_csv(here::here('dataset','leave.csv')) %>%
  rename(State = o_state_name) %>% 
  mutate(State = toupper(State))
leave$State <- gsub(' ','',leave$State)
movein <- read_csv(here::here('dataset','movein.csv')) %>%
  rename(State = d_state_name) %>% 
  mutate(State = toupper(State))
movein$State <- gsub(' ','',movein$State)
# crime rate vs leave proportion by year
leave_crime <- read_csv(here::here('dataset','00-07Crime.csv')) %>%
  rename(State=Area)%>%
  inner_join(leave,by='State')


leave_crime<- leave_crime %>% 
  pivot_longer(c(Robbery,Burglary),names_to="crime",values_to="value")
g <- ggplot(leave_crime, aes(x = value, y = proportion, color = crime,
  text = paste('population left',leave_pop, "<br>", 'total population',total_pop))) +
  geom_point(position = "jitter")+
  facet_grid(vars(year)) +
  labs(x="Crime Rate (Per 100,000 Inhabitants)",y="Proportion of 16-26 Population Leaving the States")
ggplotly(g, tooltip = "text")
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
movein_crime <- read_csv(here::here('dataset','10-17Crime.csv')) %>%
  inner_join(movein,by='State')

movein_crime<- movein_crime %>% 
  pivot_longer(c(Robbery,Burglary),names_to="crime",values_to="value")
f <- ggplot(movein_crime, aes(x = value, y = proportion, color = crime,
  text = paste('population moved in',movein_pop, "<br>", 'total population',total_pop))) +
  geom_point(position = "jitter")+
  facet_grid(vars(year))+
  labs(x="Crime Rate (Per 100,000 Inhabitants)",y="Proportion of 16-26 Population Move into the States")
ggplotly(f, tooltip = "text")
```

The non-significant associations are due to the population characteristics. Our selected population were around 16 and 26 years old at two different time points, so the crime rate might not be one of the fundamental reasons that drove them to migrate. We assume that seeking further education and working opportunities might contribute more to the decision making process of migration among people of those age groups. 

[Previous Page: Model Analysis on Demographics](/analysis3/)

[Next Page: Model Analysis on Migration Factors](/analysis5/)

