---
title: Analysis
description:
toc: true
authors: []
tags: []
categories: []
series: []
date: 2022-12-13T22:59:03-05:00
lastmod: 2022-12-13T22:59:03-05:00
featuredVideo:
featuredImage:
draft: false
---
```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
```
<font size="5"><b>Exploratory Data Analysis</font></b>


To analyze our hypothesis, we select our variables from Migration Patterns and FBI Hate Crime datasets. The Crime rate was collected by FBI. The migration pattern was collected by three organizations: Policy Impacts, Opportunity Insights and United States Census Bureau to analyze the migration between teenager and young adulthood. Our race variables was collected by collecting self-report race. The questions are “how would you identify yourself/what is your race?” Participants were asked to select from “White”, “Black”, “Hispanic”, “Asian”, and “Other”. Our income variable was collected by self-reported income level, and the researchers categorized them into five quantiles, with Q1 being the poorest and Q5 being the richest. 


We started our analysis by exploring the demographic characteristics and migration patterns. The first bar chart illustrated the proportion of different races within each state. From the graph, we can identify that Whites were dominant among all states, with Blacks and Hispanics following up. It correctly reflects the demographics of our participants at the age of 26, with Whites being dominant. New York and California are the top two destination where people tend to move to at age 16-26.
```{r echo=FALSE, fig.height=5, fig.width=5, message=FALSE, warning=FALSE}
o_MA <- read_csv(here::here("dataset","o_MA.csv"))
o_MA %>%
  group_by(d_state_name) %>%
  mutate(sum_n = sum(n)) %>%
  ungroup() %>%
  group_by(d_state_name,race) %>%
  mutate(state_race_pop = sum(n)) %>%
  summarize(sum_n=sum_n,state_race_pop=state_race_pop) %>%
  distinct(d_state_name,race,.keep_all = T) %>%
  filter(d_state_name != "Massachusetts") %>%
  ungroup() %>%
  arrange(desc(sum_n)) %>%
  filter(sum_n > 1650) %>% 
  ggplot() +
  geom_col(aes(x=reorder(d_state_name,sum_n),y=state_race_pop,fill=race))+
  theme(axis.text.x = element_text(angle=45,vjust=1,hjust=1)) +
  labs(title = "Population(Age 16-26) Moved From MA to Other States in the U.S.",
       x = "Destination State", y = "Population From MA to Other States", color="race") + 
  theme(plot.title = element_text(hjust = 0.5))
```

We also made separate pie charts to see if the migration patterns of each state can be differentiated by racial groups. We found that among 50 different destination states, white group people are the most likely to migrate. Moreover, white group people make up at least 75 percent of the total migration in each state, except Alabama, Florida, and Georgia. Asian and colored groups have relatively similar migration patterns in most states. Such distributions might be explained by the historical reasons, as Alabama, Florida, and Georgia were once slave states, thus having more black residents. 

```{r echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
o_MA %>%
  filter(d_state_name!="Massachusetts") %>%
  group_by(d_state_name,race) %>%
  summarize(state_race_pop = sum(n)) %>%
  ggplot() +
  geom_col(aes(x=1,y=state_race_pop,fill=race),position = "fill") +
  facet_wrap(~d_state_name) +  
  coord_polar(theta = "y") +
  labs(title = "Migration Race Proportion By Destination States", x="",y="",fill="Race")+
  theme(plot.title = element_text(hjust = 0.5))
```

We then further explored whether the migration patterns of each state would be differentiated by income levels. We found that among 50 states’ migration population, the Q1 income group (poorest parental income quantile) has the lowest migrant population in most cases. Surprisingly, the migration pattern in 10 of the states is very similar: people from 5 different income groups contribute a relatively equal number of the migrating population. The graph illustrating the patterns and the difference is below.

```{r echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
o_MA %>%
  filter(d_state_name!="Massachusetts") %>%
  group_by(d_state_name,income) %>%
  summarize(state_inc_pop = sum(n)) %>%
  ggplot() +
  geom_col(aes(x=1,y=state_inc_pop,fill=income),position = "fill") +
  facet_wrap(~d_state_name) +  
  coord_polar(theta = "y")+
  labs(title="Migration Parental Income Quantile Proportion By Destination States",
       x = "", y="",fill="Income (Q1=poorest,Q5=richest)") + 
   theme(plot.title = element_text(hjust = 0.5))
```


[Previous Page: Introduction](/analysis/)

[Next Page: Model Analysis](/analysis3/)