---
title: Analysis
description:
toc: true
authors: []
tags: []
categories: []
series: []
date: 2022-12-14T00:53:24-05:00
lastmod: 2022-12-14T00:53:24-05:00
featuredVideo:
featuredImage:
draft: false
---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(plotly)
library(tidyverse)
library(readr)
for_interactive<-read_csv(here::here("dataset/for_interactive.csv"))
```

<font size="5"><b>Crime Association Analysis</font></b>


To continue testing our hypothesis that crime rate is associated with the migration pattern and whether race and income would influence such association, we designed interactive plots to better illustrate the associations between the two selected crime rates (robbery and burglary) and proportion of people moved in and out of the state. By clicking the specific points on our interactive plots, one would see the exact proportion of people moved in or out of the state corresponding to the crime rate. Again, as there were no distinct patterns on our plot, we did not find evidence to support our hypothesis that the crime rate is associated with the migration patterns of the residents in the United States.

```{r echo=FALSE, message=FALSE, warning=FALSE}
leave <- read_csv(here::here('dataset','leave.csv')) %>%
  rename(State = o_state_name) %>% 
  mutate(State = toupper(State))
leave$State <- gsub(' ','',leave$State)
movein <- read_csv(here::here('dataset','movein.csv')) %>%
  rename(State = d_state_name) %>% 
  mutate(State = toupper(State))
movein$State <- gsub(' ','',movein$State)
# crime rate vs leave proportion by year
leave_crime <- read_csv(here::here('dataset','00-07Crime.csv')) %>%
  rename(State=Area)%>%
  inner_join(leave,by='State')

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
movein_crime <- read_csv(here::here('dataset','10-17Crime.csv')) %>%
  inner_join(movein,by='State')

```


```{r echo=FALSE, message=FALSE, warning=FALSE}
a1 <- for_interactive %>% pivot_longer(c(early_meanRobbery,early_meanBurglary),names_to = 'crimeType',values_to = 'crimeRate')
plot_ly(a1, type = "scatter", mode = "markers",
  x = ~jitter(crimeRate, 2), y = ~jitter(prop_leave,2), color = ~crimeType,
  text = ~paste(Area, "<br>", prop_leave),
  hovertemplate = "%{text}") %>%
  layout(xaxis = list(title = "Early years crime rate"), yaxis = list(title = "proportion of people moved out of State"))
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
a1 <- for_interactive %>% pivot_longer(c(later_meanRobbery,later_meanBurglary),names_to = 'crimeType',values_to = 'crimeRate')
plot_ly(a1, type = "scatter", mode = "markers",
  x = ~jitter(crimeRate, 2), y = ~jitter(prop_movein,2), color = ~crimeType,
  text = ~paste(Area, "<br>", prop_movein),
  hovertemplate = "%{text}") %>%
  layout(xaxis = list(title = "Later years crime rate"), yaxis = list(title = "proportion of people moved into the State"))
```


[Previous Page: Model Analysis on Demographics](/analysis3/)

[Next Page: Model Analysis on Migration Factors](/analysis5/)

